Source Code Volatility Metric

### 2020-04-17 paper/article.tex
cite

There are a few existing code change metrics, including code churn~\citep{munson1998}
and others~\citep{fentonsoftware}.

@@

It was demonstrated that the size of the source code is an important
factor negatively affecting maintainability and other quality characteristicts.
For example, \citep{heitlager2007} suggested to consider ``volume'' (the amount of code
in the repository) as a primary contributor to an aggregate maintainability index
of a software because ``it is fairly intuitive that the total size of a system should
feature heavily in any measure of maintainability.''

>>>>

The metric introduced in this research belongs to the family of
``code change metrics,'' which analyze the history of changes in a repository~\citep{fentonsoftware}.
Code churn is one of the simplest metric, which counts
all lines being modified (added, edited, and deleted) during
the entire lifetime of a project~\citep{munson1998}.
The number of changes being made to a particular file, class, method
or line of code is yet another simple metric, used for example by~\citet{demeyer2000}
in order to analyze the effect of refactorings.

\citep{biazzini2014} introduced a number of metrics to analyze
Git history (specifically related to GitHub), such as unique-count, unique-ratio,
VIP-count, VIP-ratio, scattered-count, pervasive-count and a few others. Some
of the metrics are supposed to be calculated for a repository together with
its forks, while others may be calculated for a single repository history.

To our knowledge, the metric introduced in this research has never been
suggested.

@@

It was demonstrated that the size of the source code is an important
factor negatively affecting maintainability and other quality characteristicts.
For example, \citet{heitlager2007} suggested to consider ``volume'' (the amount of code
in the repository, the number of lines per file, the number of methods in a class,
and so on) as a primary contributor to an aggregate maintainability index
of a software because ``it is fairly intuitive that the total size of a system should
feature heavily in any measure of maintainability.''
